\documentclass[12]{article}
\begin{document}
\begin{titlepage}
\huge{\bfseries Report on the Best Places to buy a Rolex}\\
\begin{flushright}
\textsc{\LARGE katambasamuel \\
214023407 \\
14/U/23285/PS\\
}
\end{flushright}
\end{titlepage}
\section{Introduction}
Rolex is one the fast foods and delicacy that is being prepared for most people who are not willing to waste time on cooking. Rolex came to existence in Uganda around the early 2000s. Basically a rolex is a combination of an omelet and vegetables wrapped with a chapatti. On 17th /August/2016, the Ugandan state minister for tourism, launched the rolex festival as effort to promote the Ugandan culture to the outside world.
\subsection{Problem Statement}
There are many issues that arise from buying rolex which may include the hygiene, prices and also the quality and quantity one is providing to the customers.
\section{General Objective}
To find out the best places to buy a rolex in terms of both quality and quantity at an affordable prices.
\subsection{Other Objectives}
\begin{itemize}
  \item To find out if the place one is buying the rolex from is convenient
  \item To find out if the place is hygienically fit for handling the delicacy.
\end{itemize}
		
\section{Methodology}
\subsection{Sampling}
Sampling or testing various Rolexes being prepared from various vendors. This was done through randomly selecting a certain number of rolex vendors within the same locality. The aims of the sampling methods were
\begin{itemize}
 \item To know the various pricing of rolex sizes
 \item To find out how different Rolexes are prepared and how they taste.
 \item To know how hygienic these rolex vendors are
 \item To know where the rolex places are located.
\end{itemize}

The sampling method was the only method used for our best rolex places survey and it was done by a group of four people who were distributed to different selected locations. They were tasked to find out the price ranges and also make critical observations on how the delicacy was prepared and also the hygiene.
\subsection{Findings from the Sampling}
\begin{itemize}
 \item Uniform prices for rolex starting from 1500/= and the price increased depending on the number of chapattis and eggs one wanted.
 \item Some vendors offer only a chapatti wrapped around the omelet minus any vegetables.
 \item Rolex vendors that provided vegetables onto their rolex always asked the customer whether to fray the vegetables within the eggs or to put it on the omelet and just wrapped it with the chapatti.
 \item There were also another kind of fast foods from the vendors like kikomando (beans and chopped chapattis), Pizza (mixture of tiny chapattis and plus omelet combined) and also rolemando (rolex plus beans)
\end{itemize}
	
\section{Conclusions and Deductions}
\begin{itemize}
 \item Places that offer vegetables in their rolex seemed to provide better quality and quantity of the delicacy.
 \item Places that had vegetables applied though vegetables onto the rolex in different ways according to the customers decision or directive.
 \item Places with limited vegetables like only onions continued to charge a uniform price like others and always complained about the high prices of vegetables to accompany the rolex.
 \item Places with limited vegetables offered low quantity and quality rolexes that were less appetizing according to the test and appearance.
\end{itemize}
\subsection{Final Remarks}
The best places to buy a delicious and satisfying rolex from, is where vegetables like cabbage, tomatoes, onions among others are fully available on the rolex vendors stall.
\end{document}

